Areal kernel demonstration

### 2022-10-27 src/0_demo_areal-kernels/areal-kernels.Rmd
Move unequal-samples development to a note in areal-kernels

Data structure for unequal number of points in each area:

>>>>

We use a start index data structure for unequal number of points in each area.
Note that other possible ways to do this include a padded data structure (`matrix(unlist(padded_sample_index), nrow = n, ncol = max_length, byrow = TRUE)`) and a database structure `group_db <- data.frame(i = unlist(sample_index), group_id = rep(seq(length(sample_index)), lengths(sample_index)))`).
